### 2015-06-06 chapters/ipa_meets_unicode.tex
updated pitfall ligatures

\begin{itemize} 
	\item <ʣ> \textsc{latin small letter dz digraph} at \uni{02A3} (use <d> + <z> instead) 
	\item <ʧ> \textsc{latin small letter tesh digraph} at \uni{02A7} (use <t> + <ʃ> instead) 
	\item <ʩ> \textsc{latin small letter feng digraph} at \uni{02A9} (use <f> + <ŋ> instead) 
\end{itemize}

>>>>

\begin{itemize} 
	\item <ʣ> \textsc{latin small letter dz digraph} at \uni{02A3} 
	  (use <dz> instead) 
    \item <ʤ> \textsc{latin small letter dezh digraph} at \uni{02A4}
      (use <dʒ> instead)
    \item <ʥ> \textsc{latin small letter dz digraph with curl} at \uni{02A5}
      (use <dʑ>)
    \item <ʦ> \textsc{latin small letter ts digraph} at \uni{02A6} 
      (use <ts> instead)
	\item <ʧ> \textsc{latin small letter tesh digraph} at \uni{02A7} 
	  (use <tʃ> instead) 
    \item <ʨ> \textsc{latin small letter tc digraph with curl} at \uni{02A8}
      (use <tɕ>)
   	\item <ʩ> \textsc{latin small letter feng digraph} at \uni{02A9}
	  (use <fŋ> instead) 
\end{itemize}
